---
title: "Evaluation Options for Trained Ensembles for COVID-19"
author: "Evan L. Ray, Estee Cramer, Nicholas G. Reich"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

<!-- Code for adding logo at the top of TOC -->

<style>
#TOC {
  background: url("https://github.com/reichlab/covid19-forecast-hub-web/raw/master/images/forecast-hub-logo_DARKBLUE-20px-padding.png");
  background-size: contain;
  padding-top: 80px !important;
  background-repeat: no-repeat;
}
</style>


This document explores some options for trained ensembles we could start using for COVID-19.

```{r include = FALSE}
# load packages
library(covidData)
library(covidEnsembles)
library(covidHubUtils)
library(tidyverse)
library(plotly)
library(gridExtra)
library(knitr)
library(DT)

knitr::opts_chunk$set(echo = FALSE, cache.lazy = FALSE)
options(width = 200)

theme_set(theme_bw())

#setwd("code/application/retrospective-qra-comparison/analyses/retrospective-scores-report/")
```

```{r include = FALSE, cache = TRUE}
# load scores
all_scores <- readRDS("../retrospective-scores/retrospective_scores.rds") %>%
  dplyr::filter(
    !grepl("ensemble_switching", model),
    !grepl("combine_method_positive", model),
    !grepl("window_size_full_history", model),
    !grepl("include_full_history_TRUE", model)#,
#    !grepl("check_missingness_by_target_TRUE", model)
  ) %>%
  dplyr::mutate(
    spatial_scale = ifelse(
      location == "US",
      "National",
      ifelse(
        nchar(location) == 2,
        "State",
        "County"
      )
    )
  )

all_model_cases <- purrr::map_dfr(
  unique(all_scores$model),
  function(x) {
    parse_model_case(x) %>% dplyr::mutate(model = x)
  }
)

all_scores <- all_scores %>%
  dplyr::left_join(all_model_cases, by = "model") %>%
  dplyr::mutate(
    target = paste(horizon, temporal_resolution, "ahead", target_variable),
    model_brief = paste(
      combine_method,
      "window",
      window_size,
      quantile_groups,
      estimation_grouping,
      sep = "_"
    )
  ) %>%
#  dplyr::filter(window_size != "full_history") %>%
  dplyr::arrange(
    combine_method,
    as.integer(window_size),
    quantile_groups,
    estimation_grouping
  )

all_models <- unique(all_scores$model_brief)
all_scores$model_brief <- factor(all_scores$model_brief, levels = all_models)
# window_10_model_inds <- grepl("window_10", all_models)
# new_levels <- c(
#   all_models[!window_10_model_inds],
#   all_models[window_10_model_inds])
```



```{r cache = TRUE}
# subset scores to those that are comparable for all models within each
# combination of spatial scale and base target
# only among those models with any forecasts for that combination
all_scores_common_by_target_variable_spatial_scale <-
  purrr::pmap_dfr(
    all_scores %>%
      distinct(target_variable, spatial_scale),
    function(target_variable, spatial_scale) {
      reduced_scores <- all_scores %>%
        dplyr::filter(
          target_variable == UQ(target_variable),
          spatial_scale == UQ(spatial_scale)
        )

      # subset to same forecasts made for each ensemble method
      scores_to_keep <- reduced_scores %>%
        dplyr::select(model, forecast_date, location, target, abs_error) %>%
        tidyr::pivot_wider(
          names_from = "model", values_from = "abs_error"
        )
      all_models <- unique(reduced_scores$model)
      scores_to_keep$keep <-
        apply(scores_to_keep[all_models], 1, function(x) all(!is.na(x)))

      # message(paste0(
      #   "at ", spatial_scale, " for ", target_variable,
      #   ", missing forecasts for models: ",
      #   paste0(
      #     all_models[apply(scores_to_keep[all_models], 2, function(x) any(is.na(x)))]
      #   )
      # ))

      scores_to_keep <- scores_to_keep %>%
        dplyr::select(forecast_date, location, target, keep)

      dplyr::left_join(
        reduced_scores,
        scores_to_keep,
        by = c("forecast_date", "location", "target")
      ) %>%
        dplyr::filter(keep) %>%
        dplyr::select(-keep)
    }
  )
```

```{r cache = TRUE}
# subset forecasts to those that are comparable for all models within each week
# only among those models with any forecasts for that week
all_scores_common_by_target_variable_spatial_scale_week <-
  purrr::pmap_dfr(
    all_scores %>%
      distinct(target_variable, spatial_scale, forecast_date) %>%
      filter(spatial_scale != "state_national"),
    function(target_variable, spatial_scale, forecast_date) {
      reduced_scores <- all_scores %>%
        dplyr::filter(
          target_variable == UQ(target_variable),
          spatial_scale == UQ(spatial_scale),
          forecast_date == UQ(forecast_date))

      # subset to same forecasts made for each ensemble method
      scores_to_keep <- reduced_scores %>%
        dplyr::select(model, forecast_date, location, target, abs_error) %>%
        tidyr::pivot_wider(
          names_from = "model", values_from = "abs_error"
        )
      all_models <- unique(reduced_scores$model)
      scores_to_keep$keep <-
        apply(scores_to_keep[all_models], 1, function(x) all(!is.na(x)))
      scores_to_keep <- scores_to_keep %>%
        dplyr::select(forecast_date, location, target, keep)

      dplyr::left_join(
        reduced_scores,
        scores_to_keep,
        by = c("forecast_date", "location", "target")
      ) %>%
        dplyr::filter(keep) %>%
        dplyr::select(-keep)
    }
  )
```


# Overall Scores {.tabset .tabset-fade}

These scores summarize model skill for each combination of base target and spatial scale.

```{r cache = TRUE, message=FALSE}
# score summaries
scores_overall <- all_scores_common_by_target_variable_spatial_scale %>%
  dplyr::mutate(
    target_variable = substr(target, regexpr(" ", target) + 1, nchar(target)),
    spatial_scale = ifelse(
      location == "US",
      "National",
      ifelse(
        nchar(location) == 2,
        "State",
        "County"
      )
    )
  ) %>%
  dplyr::group_by(
    model, model_brief, intercept, combine_method, missingness, quantile_groups,
    window_size, check_missingness_by_target, do_standard_checks,
    do_baseline_check, estimation_grouping, target_variable, spatial_scale) %>%
  dplyr::summarize(
    across(starts_with("abs_error"), function(x) round(mean(x), 3)),
    across(starts_with("wis"), function(x) round(mean(x), 3)),
    across(starts_with("coverage"), function(x) round(mean(x), 3))#,
  )

scores_by_week <- all_scores_common_by_target_variable_spatial_scale_week %>%
  dplyr::mutate(
    target_variable = substr(target, regexpr(" ", target) + 1, nchar(target)),
    spatial_scale = ifelse(
      location == "US",
      "National",
      ifelse(
        nchar(location) == 2,
        "State",
        "County"
      )
    )
  ) %>%
  dplyr::group_by(
    model, model_brief, intercept, combine_method, missingness, quantile_groups,
    window_size, check_missingness_by_target, do_standard_checks,
    do_baseline_check, forecast_date, estimation_grouping, target_variable, spatial_scale) %>%
  dplyr::summarize(
    across(starts_with("abs_error"), function(x) round(mean(x), 3)),
    across(starts_with("wis"), function(x) round(mean(x), 3)),
    across(starts_with("coverage"), function(x) round(mean(x), 3))#,
  )

scores_by_location_week <- all_scores_common_by_target_variable_spatial_scale_week %>%
  dplyr::filter(nchar(location) == 2) %>%
  dplyr::mutate(
    target_variable = substr(target, regexpr(" ", target) + 1, nchar(target)),
    spatial_scale = ifelse(
      location == "US",
      "National",
      ifelse(
        nchar(location) == 2,
        "State",
        "County"
      )
    )
  ) %>%
  dplyr::group_by(
    model, model_brief, intercept, combine_method, missingness, quantile_groups,
    window_size, check_missingness_by_target, do_standard_checks,
    do_baseline_check, forecast_date, estimation_grouping, target_variable, location) %>%
  dplyr::summarize(
    across(starts_with("abs_error"), function(x) round(mean(x), 3)),
    across(starts_with("wis"), function(x) round(mean(x), 3)),
    across(starts_with("coverage"), function(x) round(mean(x), 3))#,
  )
```

For brevity, we'll look here at performance for a subset of the variations on "trained" approaches that we have considered.
Below are the settings we're examining, and reasons we chose them from among the alternatives.

 * We use the constraint that the model weights are non-negative and sum to 1, and we do not include an intercept.  A more flexible variation only enforces that the weights are non-negative and includes an intercept; overall, the performance of this method can slightly better for cases than the convex versions, but its performance seems less stable, with a lot of variation in performance for different window sizes -- and it is consistently much worse for deaths.  I have stuck with the more constrained method with more stable performance.
 * Missing forecasts are mean-imputed and then weights are redistributed according to missingness levels; this approach has limitations and needs refinement, but has been better than performing estimation separately for each group of locations with complete data in every evaluation I've looked at.
 * We do not employ any checks of model forecasts other than the validations performed on submission.  I have not looked at approaches using these checks recently, but in analyses from a few months ago they were not very helpful for trained ensembles.

Within these settings, we explore variations in the training set window size (the number of past weeks of forecasts used to estimate ensemble weights).

We also consider three quantile grouping strategies: "per model" weights, "per quantile" approaches where there is a separate weight parameter for each combination of model and quantile level, and "3 groups" of quantile levels: the three lowest, the three highest, and the middle ones.

We compare to two "untrained" ensembles: an equally-weighted mean (`ew`) at each quantile level and a `median` at each quantile level.

We perform estimation either separately for each spatial scale (National, State, and County), or jointly across the State and National levels.

The overall average scores in the tables below are computed across a comparable set of forecasts for all models, determined by the model evaluated with the fewest available forecasts (corresponding to a training set window of 10).  For incident deaths, the relative rankings of median and mean ("ew") can change as a few more weeks are added or removed from the evaluation set.  Per-week scores plotted further down are computed across a comparable set of forecasts for all models that are available within each week.

## Incident Cases  {.tabset .tabset-fade}


###National 
National level mean scores across comparable forecasts for all methods.
```{r}
overall_rankings_inc_case_national <- scores_overall %>%
  filter(
    spatial_scale == "National",
    target_variable == "wk ahead inc case") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis)

DT::datatable(overall_rankings_inc_case_national %>%
  select(-model_brief))
```

###State
State level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_inc_case_state <- scores_overall %>%
  filter(
    spatial_scale == "State",
    target_variable == "wk ahead inc case") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis)

DT::datatable(overall_rankings_inc_case_state %>%
  select(-model_brief))
```

###County
County level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_inc_case_county <- scores_overall %>%
  filter(
    spatial_scale == "County",
    target_variable == "wk ahead inc case") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis) %>%
  as.data.frame()

DT::datatable(overall_rankings_inc_case_county %>%
  select(-model_brief))
```

## Incident Hospitalizations  {.tabset .tabset-fade}

###National
National level mean scores across comparable forecasts for all methods.
```{r}
overall_rankings_inc_hosp_national <- scores_overall %>%
  filter(
    spatial_scale == "National",
    target_variable == "day ahead inc hosp") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis)

DT::datatable(overall_rankings_inc_hosp_national %>%
  select(-model_brief))
```

###State
State level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_inc_hosp_state <- scores_overall %>%
  filter(
    spatial_scale == "State",
    target_variable == "day ahead inc hosp") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis)

DT::datatable(overall_rankings_inc_hosp_state %>%
  select(-model_brief))
```

## Incident Deaths  {.tabset .tabset-fade}

###National
National level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_inc_death_national <- scores_overall %>%
  filter(
    spatial_scale == "National",
    target_variable == "wk ahead inc death") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis) %>%
  as.data.frame()

DT::datatable(overall_rankings_inc_death_national %>%
  select(-model_brief))
```


###State
State level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_inc_death_state <- scores_overall %>%
  filter(
    spatial_scale == "State",
    target_variable == "wk ahead inc death") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis) %>%
  as.data.frame()

DT::datatable(overall_rankings_inc_death_state %>%
  select(-model_brief))
```

## Cumulative Deaths  {.tabset .tabset-fade}

### National
National level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_cum_death_national <- scores_overall %>%
  filter(
    spatial_scale == "National",
    target_variable == "wk ahead cum death") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis) %>%
  as.data.frame()

DT::datatable(overall_rankings_cum_death_national %>%
  select(-model_brief))
```

### State
State level mean scores across comparable forecasts for all methods:

```{r}
overall_rankings_cum_death_state <- scores_overall %>%
  filter(
    spatial_scale == "State",
    target_variable == "wk ahead cum death") %>%
  ungroup() %>%
  select(
    model_brief, combine_method, estimation_grouping, quantile_groups,
    window_size, wis, mae = abs_error,
    coverage_50, coverage_80, coverage_95) %>%
  arrange(wis) %>%
  as.data.frame()

DT::datatable(overall_rankings_cum_death_state %>%
  select(-model_brief))
```


The high WIS for the equal weighted mean here is not a bug -- one forecast was crazy high in the upper tail; this shows up in WIS but not in the other metrics.

# Plots showing scores by week {.tabset .tabset-fade}

In these plots we show results for the mean, median, and the top-performing convex approach within each combination of base target and spatial scale.

For readability, we also drop the score for the unweighted mean ensemble forecast of state level cumulative deaths in the week where that method had very high WIS.

```{r}
reduced_scores_by_week <- scores_by_week %>%
  dplyr::ungroup() %>%
  dplyr::filter(
    combine_method %in% c("ew", "median") |
    (spatial_scale == "National" & target_variable == "wk ahead inc case" &
      model_brief == overall_rankings_inc_case_national %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "State" & target_variable == "wk ahead inc case" &
      model_brief == overall_rankings_inc_case_state %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "County" & target_variable == "wk ahead inc case" &
      model_brief == overall_rankings_inc_case_county %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "National" & target_variable == "day ahead inc hosp" &
      model_brief == overall_rankings_inc_hosp_national %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "State" & target_variable == "day ahead inc hosp" &
      model_brief == overall_rankings_inc_hosp_state %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "National" & target_variable == "wk ahead inc death" &
      model_brief == overall_rankings_inc_death_national %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "State" & target_variable == "wk ahead inc death" &
      model_brief == overall_rankings_inc_death_state %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "National" & target_variable == "wk ahead cum death" &
      model_brief == overall_rankings_cum_death_national %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1)) |
    (spatial_scale == "State" & target_variable == "wk ahead cum death" &
      model_brief == overall_rankings_cum_death_state %>%
        dplyr::filter(!(combine_method %in% c("ew", "median"))) %>%
        dplyr::pull(model_brief) %>%
        `[`(1))
  ) %>%
  dplyr::mutate(
    wis = ifelse(wis < 10000000, wis, NA_real_),
    spatial_scale = factor(
      spatial_scale,
      levels = c("National", "State", "County")),
    target_variable = factor(
      target_variable,
      levels = c("wk ahead inc case", "day ahead inc hosp", "wk ahead inc death",
        "wk ahead cum death"))
  )
```

## WIS by week

```{r fig.width=10, fig.height=10}
# all scores by week
ggplot(data = reduced_scores_by_week) +
  geom_line(mapping = aes(
    x = factor(forecast_date),
    y = wis,
    # color = model,
    # linetype = model,
    # group = model)) +
    color = combine_method,
    linetype = combine_method,
    group = combine_method)) +
  facet_wrap( ~ spatial_scale + target_variable, scales = "free_y", ncol = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## MAE by week

```{r fig.width=10, fig.height=10}
# all scores by week
ggplot(data = reduced_scores_by_week %>% mutate(mae = abs_error)) +
  geom_line(mapping = aes(
    x = forecast_date,
    y = mae,
    color = combine_method,
    linetype = combine_method,
    group = combine_method)) +
  facet_wrap( ~ spatial_scale + target_variable, scales = "free_y", ncol = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


## Two-sided interval coverage by week: {.tabset .tabset-fade}

### 50% 

```{r fig.width=10, fig.height=10}
# all scores by week
ggplot(data = reduced_scores_by_week) +
  geom_line(mapping = aes(
    x = forecast_date,
    y = coverage_50,
    color = combine_method,
    linetype = combine_method,
    group = combine_method)) +
  geom_hline(yintercept = 0.5) +
  ylim(c(0, 1)) +
  facet_wrap( ~ spatial_scale + target_variable, scales = "free_y", ncol = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


### 80%

```{r fig.width=10, fig.height=10}
# all scores by week
ggplot(data = reduced_scores_by_week) +
  geom_line(mapping = aes(
    x = forecast_date,
    y = coverage_80,
    color = combine_method,
    linetype = combine_method,
    group = combine_method)) +
  geom_hline(yintercept = 0.8) +
  ylim(c(0, 1)) +
  facet_wrap( ~ spatial_scale + target_variable, scales = "free_y", ncol = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```



### 95%

```{r fig.width=10, fig.height=10}
# all scores by week
ggplot(data = reduced_scores_by_week) +
  geom_line(mapping = aes(
    x = forecast_date,
    y = coverage_95,
    color = combine_method,
    linetype = combine_method,
    group = combine_method)) +
  geom_hline(yintercept = 0.95) +
  ylim(c(0, 1)) +
  facet_wrap( ~ spatial_scale + target_variable, scales = "free_y", ncol = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


# Forecast Score Availablity

This section displays heat maps showing score availability by date, target_variable, spatial scale, and model.
In each cell, we expect to see a number of scores equal to the number of locations for the given spatial scale times
the number of horizons for the given target.

##All forecasts {.tabset .tabset-fade}

###County
```{r fig.width=10, fig.height=2}
score_counts <- all_scores %>%
  dplyr::count(
    forecast_date,
    target_variable,
    spatial_scale,
    model_brief
  )

score_counts %>%
  dplyr::filter(spatial_scale == "County") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("County Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

###State
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "State") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("State Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

###National
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "National", grepl("death", target_variable)) %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("National Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```



## Forecasts available for all models that are available within each combination of base target and spatial scale {.tabset .tabset-fade}

Here we have subset the forecasts to those that are comparable across all models within each combination of base target and spatial scale.
We expect to see the exact same score counts for all models within each plot facet.
Average scores computed within a combination of base target and spatial scale will be comparable.

### County
```{r fig.width=10, fig.height=2}
score_counts <- all_scores_common_by_target_variable_spatial_scale %>%
  dplyr::count(
    forecast_date,
    target_variable,
    spatial_scale,
    model_brief
  )

score_counts %>%
  dplyr::filter(spatial_scale == "County") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("County Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

### State
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "State") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("State Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

### National
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "National") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("National Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## Forecasts available for all models that are available within each combination of base target, spatial scale, and week {.tabset .tabset-fade}

Here we have subset the forecasts to those that are comparable across all models within each combination of base target, spatial scale, and week.
We expect to see the exact same score counts within each column of the plot, for all models for which any forecasts are available.
Average scores computed within a combination of base target, spatial scale, and forecast week will be comparable.

###County
```{r fig.width=10, fig.height=2}
score_counts <- all_scores_common_by_target_variable_spatial_scale_week %>%
  dplyr::count(
    forecast_date,
    target_variable,
    spatial_scale,
    model_brief
  )

score_counts %>%
  dplyr::filter(spatial_scale == "County") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("County Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

###State
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "State") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("State Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

###National
```{r fig.width=10, fig.height=16}
score_counts %>%
  dplyr::filter(spatial_scale == "National") %>%
  ggplot() +
    geom_raster(mapping = aes(
      x = factor(forecast_date), y = model_brief, fill = factor(n)
    )) +
    facet_wrap( ~ target_variable, ncol = 1) +
    ggtitle("National Level Forecast Availability") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

