---
title: "Quantile Regression Averaging"
author: "Evan L. Ray"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=T}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

\def\simiid{\stackrel{{\mbox{\text{\tiny i.i.d.}}}}{\sim}}

# Introduction

The purpose of this document is to demonstrate and verify the functionality of the package with a few simple simulated examples.

We will use the following packages:

```{r packages}
library(covidEnsembles)
library(zeallot)
library(tidyverse)
library(gridExtra)
```

# Simple QRA Example

We consider QRA for the following scenario:

 * The observed training data are $X_1, \ldots, X_{100} \simiid \text{Normal}(0, 1)$
 * We have three misspecified predictive models:
    * **wide:** $P_1 = \text{Normal}(0.0, \sqrt{2})$
    * **narrow:** $P_2 = \text{Normal}(0.0, \sqrt{0.5})$
    * **bias\_wide:** $P_3 = \text{Normal}(0.2, \sqrt{2})$

The pdfs for these distributions are illustrated below:

```{r}
model_params <- data.frame(
  model = c('DGP', 'Wide', 'Narrow', 'Bias_Wide'),
  mean = c(0.0, 0.0, 0.0, 0.5),
  sd = c(1.0, sqrt(2), sqrt(0.5), sqrt(2)),
  stringsAsFactors = FALSE
)

x_grid <- seq(from=-3, to=3, length=201)
curves <- purrr::pmap_dfr(
  model_params,
  function(model, mean, sd) {
    data.frame(
      model = model,
      x = x_grid,
      pdf = dnorm(x_grid, mean=mean, sd=sd),
      cdf = pnorm(x_grid, mean=mean, sd=sd)
    )
  })

p1 <- ggplot(data = curves,
       mapping = aes(x = x, y = pdf, color=model, linetype=model)) +
  geom_line() +
  theme_bw() +
  ggtitle('Probability Density Functions')

p2 <- ggplot(data = curves,
       mapping = aes(x = x, y = cdf, color=model, linetype=model)) +
  geom_line() +
  theme_bw() +
  ggtitle('Cumulative Distribution Functions')

grid.arrange(p1, p2)
```

Throughout, we evaluate forecast skill with the weighted interval score (WIS) based on the following quantile levels:

```{r}
c(0.01, 0.025, seq(0.05, 0.95, by = 0.05), 0.975, 0.99)
```

## Train and test set set up, component model predictions

We simulate $n_{train}=10^2$ observations for the training set used to estimate quantile regression averaging parameters, and $n_{test} = 10^4$ observations for the purpose of evaluating performance.

```{r}
set.seed(7462934) # mashed keyboard for science
n_train <- 10^2
y_train <- rnorm(n_train)

n_test <- 10^4
y_test <- rnorm(n_test)
```

For all observations, the predictive quantiles from the three component models are the same.  We assemble training and test set QuantileForecastMatrix objects representing these predictions.

```{r}
make_predictive_quantile_objects <- function(n) {
  predictive_quantiles_df <- expand.grid(
    obs_ind = seq_len(n),
    model = model_params$model,
    quantile_level = c(0.01, 0.025, seq(0.05, 0.95, by = 0.05), 0.975, 0.99),
    stringsAsFactors = FALSE
  ) %>%
    left_join(model_params, by='model') %>%
    mutate(quantile_value = qnorm(quantile_level, mean=mean, sd=sd)) %>%
    select(-mean, -sd)
  
  qfm <- new_QuantileForecastMatrix_from_df(
    predictive_quantiles_df %>% filter(model != 'DGP'),
    model_col = 'model',
    id_cols = c('obs_ind'),
    quantile_name_col = 'quantile_level',
    quantile_value_col = 'quantile_value'
  )
  
  qfm_per_model <- purrr::map(
    model_params$model,
    function(model) {
      new_QuantileForecastMatrix_from_df(
        predictive_quantiles_df %>% filter(model == UQ(model)),
        model_col = 'model',
        id_cols = c('obs_ind'),
        quantile_name_col = 'quantile_level',
        quantile_value_col = 'quantile_value'
      )
    }
  ) %>%
    `names<-`(model_params$model)
  
  return(c(list(predictive_quantiles_df, qfm), qfm_per_model))
}

c(train_predictive_quantiles_df,
  train_qfm,
  train_qfm_DGP,
  train_qfm_Wide,
  train_qfm_Narrow,
  train_qfm_Bias_Wide) %<-% make_predictive_quantile_objects(n_train)

c(test_predictive_quantiles_df,
  test_qfm,
  test_qfm_DGP,
  test_qfm_Wide,
  test_qfm_Narrow,
  test_qfm_Bias_Wide) %<-% make_predictive_quantile_objects(n_test)
```

Here are test set scores for the four models individually:

```{r}
test_scores <- model_params['model'] %>%
  mutate(
    wis = purrr::map_dbl(
      model,
      function(model) {
        mean(wis(y_test, get(paste0('test_qfm_', model))))
      }
    )
  )
test_scores
```

## QRA Method 1: Equally weighted combination of misspecified models

```{r}
ew_qra_fit <- estimate_qra(qfm_train = train_qfm, qra_model = 'ew')
test_qfm_EW_QRA <- predict(ew_qra_fit, test_qfm)
```

```{r}
test_scores <- data.frame(model = c('DGP', 'Wide', 'Narrow', 'Bias_Wide', 'EW_QRA')) %>%
  mutate(
    wis = purrr::map_dbl(
      model,
      function(model) {
        mean(wis(y_test, get(paste0('test_qfm_', model))))
      }
    )
  )
test_scores
```


## QRA Method 2: Convex Combination of misspecified models, one weight per model across all quantile levels

```{r}
convex_qra_fit <- estimate_qra(qfm_train = train_qfm, y_train = y_train, qra_model = 'convex_per_model')
test_qfm_Convex_QRA <- predict(convex_qra_fit[[2]], test_qfm)
```

```{r}
test_scores <- data.frame(model = c('DGP', 'Wide', 'Narrow', 'Bias_Wide', 'EW_QRA', 'Convex_QRA')) %>%
  mutate(
    wis = purrr::map_dbl(
      model,
      function(model) {
        mean(wis(y_test, get(paste0('test_qfm_', model))))
      }
    )
  )
test_scores
```

