---
title: "Simulation Study models"
author: "Evan L. Ray"
date: "5/28/2020"
output: pdf_document
---

\def\logit{\text{logit}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, cache=TRUE)
```

```{r}
library(tidyverse)
```

# Some Exploratory Plots

```{r}
covid <- read_csv('../../../data-raw/jhu-incident.csv')
pops <- read_csv('../../../data-raw/location_traits.csv')
covid <- covid %>%
  dplyr::left_join(
    pops %>%
      select(
        location_abbreviation=postalCode,
        pop=totalpop
      ))
```


```{r, fig.width=7, fig.height=9}
ggplot(
  data = covid,
  mapping = aes(x = week, y = value, group=location)) +
  geom_line() +
  facet_wrap( ~ location_abbreviation, scales = 'free_y') +
  ggtitle('incident deaths, vertical scale per location')
```

```{r, fig.width=7, fig.height=9}
ggplot(
  data = covid,
  mapping = aes(x = week, y = value, group=location)) +
  geom_line() +
  facet_wrap( ~ location_abbreviation) +
  ggtitle('incident deaths, same vertical scale')
```

```{r, fig.width=7, fig.height=9}
ggplot(
  data = covid,
  mapping = aes(x = week, y = value/pop, group=location)) +
  geom_line() +
  facet_wrap( ~ location_abbreviation) +
  ggtitle('incident deaths/population, same vertical scale')
```

Observations:

 * We have integer counts of deaths
 * scaling by population is helpful.


# Models

## SIRD fit separately by state

Notation:

 * $N$ = population for location
 * $y(t)$ = count of deaths for location at time $t$
 * $s(t)$ = proportion of population susceptible at time $t$
 * $i(t)$ = proportion of population infected at time $t$
 * $r(t)$ = proportion of population recovered at time $t$
 * $d(t)$ = proportion of population dead at time $t$

Model:

\begin{align*}
y(t) &\sim \text{Negative Binomial}\left(\{d(t) - d(t-1)\}N, \phi\right) \\
\frac{d}{dt} s(t) &= - \beta s(t) i(t) \\
\frac{d}{dt} i(t) &= \beta s(t) i(t) - \gamma i(t) - \mu i(t) \\
\frac{d}{dt} r(t) &= \gamma i(t) \\
\frac{d}{dt} d(t) &= \mu i(t) \\
\end{align*}

Priors:

\begin{align*}
d(0) &= 0.0 \\
\tilde{s}(0) &\sim \text{Normal}(\nu_s, \sigma^2_s) \\
\nu_s &\sim \text{Normal}(7.0, 2.0) \\
\sigma_s &\sim \text{Gamma}(1, 1) \\
\tilde{i}(0) &\sim \text{Normal}(\nu_s, \sigma^2_s) \\
\nu_i &\sim \text{Normal}(0.0, 2.0) \\
\sigma_i &\sim \text{Gamma}(1, 1) \\
\tilde{r}(0) &= 0.0 \\
\begin{bmatrix}s(0) \\ i(0) \\ r(0) \end{bmatrix} &= \text{softmax}\left( \begin{bmatrix}\tilde{s}(0) \\ \tilde{i}(0) \\ \tilde{r}(0) \end{bmatrix} \right) \\
\log(\beta) &\sim \text{Normal}(\nu_{\beta}, \sigma^2_{\beta}) \\
\nu_{\beta} &\sim \text{Normal}(0.33, 2) \\
\sigma_{\beta} &\sim \text{Gamma}(1, 1) \\
\log(\gamma) &\sim \text{Normal}(\nu_{\gamma}, \sigma^2_{\gamma}) \\
\nu_{\gamma} &\sim \text{Normal}(-0.7, 2) \\
\sigma_{\gamma} &\sim \text{Gamma}(1, 1) \\
\log(\mu) &\sim \text{Normal}(\nu_{\mu}, \sigma^2_{\mu}) \\
\nu_{\mu} &\sim \text{Normal}(-7.5, 2) \\
\sigma_{\mu} &\sim \text{Gamma}(1, 1) \\
\log(\phi) &\sim \text{Normal}(\nu_{\phi}, \sigma^2_{\phi}) \\
\nu_{\phi} &\sim \text{Normal}(1, 2) \\
\sigma_{\phi} &\sim \text{Gamma}(1, 1) \\
\end{align*}

